DeepSphere: a graph-based spherical CNN

### 2020-12-30 main.tex
fix: iclr2020_conference.sty was renamed to iclr2020.sty
be a bit more specific about likelihood-free inference and summary statistics

\documentclass{article} % For LaTeX2e
\usepackage{iclr2020_conference,times}

@@

Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
% such as Approximate Bayesian computation (ABC)
As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps instead \citep{schmelze2017cosmologicalmodel}.
We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $3.5$ (i.e., the signal is hidden in noise of $3.5$ times higher standard deviation).
% 60 maps * 12 parts = 720 parts
Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.

@@

\bibliography{references}
\bibliographystyle{iclr2020_conference}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr2020,times}

@@

Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
Those parameters are estimated by likelihood-free inference, which requires a method to extract summary statistics to compare simulations and observations.
As the sufficient and most concise summary statistics are the parameters themselves, one desires a method to predict them from simulations.
% such as Approximate Bayesian computation (ABC)
As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps instead \citep{schmelze2017cosmologicalmodel}.
We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps made of $n \approx 10^6$ pixels ($1/12 \approx 8\%$ of a sphere at $N_{side} = 1024$) from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $3.5$ (i.e., the signal is hidden in noise of $3.5$ times higher standard deviation).
% 60 maps * 12 parts = 720 parts
Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.

@@

\bibliography{references}
\bibliographystyle{iclr2020}
